Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-07-02 kappa.tex
Activate endfloat.
Add figures in field area description.

@@

% Finally to not include graphics
%\renewcommand{\includegraphics}[2][,]{}
%\renewcommand{\subgraphics}[3][,]{}
%\usepackage{endfloat}
%\renewcommand{\efloatseparator}{\mbox{}}

@@

\todo{Figure. Location map of North America}\\
\todo{Figure. Topographic map of the Cordillera}\\

@@

\todo{Figure. Cordillera wet climate photo}\\
\todo{Figure. Cordillera dry climate photo}\\
\todo{Figure. Climatic patters}

@@

\todo{Figure. Glacierized region photo}\\
\todo{Figure. Tuya Lake moraine photo}\\
\todo{Figure. Meltwater channels photo}\\
\todo{Figure. Lineation map}

>>>>

% Move floats to the end
\usepackage[nolists]{endfloat}
\renewcommand{\efloatseparator}{\mbox{}}

@@

% Finally to not include graphics
%\renewcommand{\includegraphics}[2][,]{}
%\renewcommand{\subgraphics}[3][,]{}

@@

% fig:locmap
\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{map-northamerica}}
  \caption{Relief map of northern North America showing a reconstruction of the
           areas covered by the Cordilleran (CIS), Laurentide (LIS), Innuitian
           (IIS) and Greenland (GIS) ice sheets during the last glacial maximum
           \citep[21.4 to 16.8\,cal\,\chem{^{14}C}\,kyr\,BP][]{Dyke.2004}.
           The rectangular box delimits the model domain used throughout this
           thesis and on which most figures were drawn. The background
           map consists of ETOPO1 \citep{Amante.Eakins.2009} and Natural Earth
           Data \citep{Patterson.Kelso.2014}.
           \todo{Mark palaeo-ice sheets on the map.}}
  \label{fig:locmap}
\end{figure}

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{map-cordillera}}
  \caption{North-oriented topographic map of the northern American Cordillera.
           Cumulative last glacial maximum ice cover from \citet{Dyke.2004}.
           The background map consists of ETOPO1 \citep{Amante.Eakins.2009}
           and Natural Earth Data \citep{Patterson.Kelso.2014}.
           \todo{Mark the main reliefs. Add model domain?}}
  \label{fig:locmap}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{photo-fraser-valley}
  \caption{This dry landscape of the Fraser Valley, central British Columbia,
           exhibits climatic contrasts at play in the Cordillera.}
  \label{fig:photo-fraser-valley}
\end{figure}

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{plot-atm}}
  \caption{Some characteristics of the Cordilleran climate according to the
           North American Regional Reanalysis
           \citep[NARR,][]{Mesinger.etal.2006}}
  \label{fig:plot-atm}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{photo-alaska-range}}
  \caption{The Alaska Range hosts several of the highest peaks in the North
           American Cordillera. Despite this fact and its northerly location,
           its North slopes hosts relatively small glaciers only, which had not
           been much more extensive during the Last Glacial Maximum
           \citep{Kaufman.Manley.2004}, indicating dry climate conditions.
           The Alaska Range is rapidly eroding, as shown by landslide-covered
           valley sides on this photograph.}
  \label{fig:photo-alaska-range}
\end{figure}

\begin{figure}
  \centering
  \makebox[0pt]{\includegraphics{photo-tuya-moraine}}
  \caption{The Tuya Lake Moraine in northern British Columbia.}
  \label{fig:photo-tuya-moraine}
\end{figure}
